How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-28 tse-paper/content.tex
Implement more fixes

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
% M: All of these are passive
% C: it says resolved, but they still are?
% M: Only the first one still is (don't know how to convert it), the others
% are not?
% I exchanged 'extracted' with targeted / analysis
% 'information retrieved' or 'information extracted' will give us
% this is not IR neither IE discussions again
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}

@@

\subsection{Descriptive Study Statistics}
To be done.

\subsection{Results}
\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}

@@

\caption{Multi-label categorization of the 61 relevant articles.}
\end{figure}

In this section, we present the results of the analysis phase of the
literature mapping along RQ 1.1 through RQ 1.3.

\subsubsection{What information is targeted in build logs? (RQ 1.1)}
The precise information targeted in the build logs varied from article
to article.
\Cref{fig:litsur:info_target} gives an overview over the frequency of
the targeted information.
Most prominent was the search for errors (39\%), followed by extracting
the executed or the failing
tests (both 11\%).
There were also numerous works which targeted more specialized
information, such as the environments used during the
build~\cite{zolfagharinia2017not}, packages
installed~\cite{selberg2012use}, or hints to source files which
relate to build failures~\cite{ren2018automated}.

\Cref{fig:litsur:use} shows the reason for the
investigated articles to analyze build logs.
The majority of articles (46\%) used the outcome of their build log
analysis to drive further research.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other articles (10\%) used the gained insights to give feedback to
developers.
For 8\% of the articles the retrieved information was the input
to a next automatic on-ward processing step.
Articles chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

We also identified the type of information which the articles
retrieved from the build logs.
In most cases (51\%), the researchers retrieved a chunk of text.
They scanned build logs for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, they distinguish failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
determine whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

\subsubsection{Which analysis techniques exist? (RQ 1.2)}
\Cref{tab:litsur:techniques} presents the techniques that the articles
described for analyzing build logs.
43 of the 61 articles we inspected mentioned how they are analyzing
build logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs''
~\cite{rahman2018impact}.
For such imprecise statements it was often not clear if they describe
a complex parser (including a tokenizer, lexer, etc.) or refer to a
simpler parsing tool based on regular expressions.
If we saw evidence for the latter, we assigned the tag
``regular expression'' instead of the tag ``parser''.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.

>>>>

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
% M: All of these are passive
% C: it says resolved, but they still are?
% M: Only the first one still is (don't know how to convert it),
% the others
% are not?
% I exchanged 'extracted' with targeted / analysis
% 'information retrieved' or 'information extracted' will give us
% this is not IR neither IE discussions again
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}

@@

\subsection{Results}
\addtolength{\tabcolsep}{-5pt}

In this section, we give a general overview over our paper population
and then present the results of the analysis phase of the literature
mapping along RQ 1.1 through RQ 1.3.

\subsection{Descriptive Study Statistics}
To be done.
% TODO moritz: age of papers (graph), kind of
% publication (master, paper)
% published (y, n)

\subsubsection{What information is targeted in build logs? (RQ 1.1)}

\caption{Multi-label categorization of the 61 relevant articles.}
\label{fig:litsur_r}
\end{figure}

In this section, we describe what sort of information papers usually
extract from build logs, along the results depicted
in \Cref{fig:litsur_r}.

\Cref{fig:litsur:info_target} gives an overview over the frequency of
the targeted information.
The precise information targeted in the build logs varied from article
to article, with a relatively long tail.
Most prominent was the search for errors (39\%), followed by extracting
the executed or the failing
tests (both 11\%).
There were also numerous works which targeted more specialized
information, such as the environments used during the
build~\cite{zolfagharinia2017not}, packages
installed~\cite{selberg2012use}, or hints to source files which
relate to build failures~\cite{ren2018automated}.

\Cref{fig:litsur:use} shows the reason for the
investigated articles to analyze build logs.
The majority of articles (46\%) used the outcome of their build log
analysis to drive further research.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other articles (10\%) used the gained insights to give feedback to
developers.
For 8\% of the articles was the retrieved information the input
to a next automatic on-ward processing step:
articles chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

% TODO Moritz: add missing figure
We also identified the type of information which the articles
retrieved from the build logs.
In most cases (51\%), the researchers retrieved a chunk of text.
They scanned build logs for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, they distinguish failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
determine whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

\subsubsection{Which analysis techniques exist? (RQ 1.2)}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}

@@

\Cref{tab:litsur:techniques} presents the techniques that the articles
described for analyzing build logs.
43 of the 61 articles we inspected mentioned how they are analyzing
build logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs''
~\cite{rahman2018impact}.
For such imprecise statements it was often not clear if they describe
a complex parser (including a tokenizer, lexer, etc.) or refer to a
simpler parsing tool based on regular expressions.
If we saw evidence for the latter, we assigned the tag
``regular expression'' instead of the tag ``parser.''
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually. For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
